volleyball dataset

### 2021-02-04 inst/volleyball.Rmd
consistentification of volleyball

This short document discusses a dataset first presented by Hankin
(2010), although here only the first 52 (out of 4000) observations are
used.

@@

The first row shows a game between a team comprising `p1`, `p4`, and
`p8` against a team comprising `p5` and `p6`.  Team `p1 p4 p8` won.
We may use function `volley()` to convert this to a likelihood
function:

>>>>

This short document discusses a dataset first presented by Hankin
(2010), although here only the first 52 observations are used.  A
volleyball \dfn{set} is a Bernoulli trial between two disjoint subsets
of the players.  The two subsets are denoted (after the game) as the
_winners_ and the _losers_: these are denoted by `1` and `0`
respectively.

@@

Each row of `volleyball_table` is a set.  Thus the first line shows a
game between a team comprising `p1`, `p4`, and `p8` against a team
comprising `p5` and `p6`.  Player `p9` did not play; team `p1 p4 p8`
won.

We may use function `volley()` to convert this to a likelihood
function:
